The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-22 src/ms.tex
Add references to body for new affiliated packages

Since \paperii, there has been an expansion of affiliated
packages for gravitational astrophysics, including:
\texttt{PyCBC} for exploring gravitational wave signals, \texttt{lenstronomy} for
modeling strong gravitational lenses, \texttt{ligo.skymap} for visualizing
gravitational wave probability maps, and \texttt{EinsteinPy} for general
relativity and gravitational astronomy. There have also been several packages
added to the ecosystem related to HEALPix: \texttt{astropy-healpix}
for a BSD-licensed HEALPix implementation, and \texttt{mocpy} for Multi-Order
Coverage maps. \texttt{astroalign} has been introduced for astrometric registration,
and \texttt{python-cpl} has been added for ESO pipelines and VLT data products.
For ground-based astronomy, \texttt{baseband} has added IO capabilities for
VLBI, and \texttt{SpectraPy} brings slit spectroscopy to the \astropy ecosystem.
Other new affiliated packages include \texttt{agnpy} for AGN jets,
\texttt{statmorph} for fitting galactic morphological diagnostics,
\texttt{dust\_extinction} for modeling interstellar dust extinction,
\texttt{feets} for extracting features from time series data, and
\texttt{corral} for managing data intensive parallel pipelines.
\texttt{casaformats-io} provides infrastructure for reading data stored in CASA table formats.
\texttt{saba} gives an interface to the Sherpa \citep{sherpa} fitting routines,
\texttt{BayesicFitting} provides an interface for generic Bayesian inference,
and \texttt{sbpy} enables calculations for asteroid and
cometary astrophysics. Finally, \texttt{synphot} provides an interface for
synthetic photometry.
% \citep{Mommert2019}

>>>>

Since \paperii, there has been an expansion of affiliated
packages for gravitational astrophysics, including:
\texttt{PyCBC} \cite{PyCBC} for exploring gravitational wave signals, \texttt{lenstronomy} \cite{lenstronomy:1} for
modeling strong gravitational lenses, \texttt{ligo.skymap} for visualizing
gravitational wave probability maps, and \texttt{EinsteinPy} \cite{EinsteinPy} for general
relativity and gravitational astronomy. There have also been several packages
added to the ecosystem related to HEALPix: \texttt{astropy-healpix}
for a BSD-licensed HEALPix implementation, and \texttt{mocpy} for Multi-Order
Coverage maps. \texttt{astroalign}  \cite{astroalign} has been introduced for astrometric registration,
and \texttt{python-cpl} products \cite{pythoncpl} has been added for ESO pipelines and VLT data.
For ground-based astronomy, \texttt{baseband} \cite{baseband} has added IO capabilities for
VLBI, and \texttt{SpectraPy} \cite{SpectraPy} brings slit spectroscopy to the \astropy ecosystem.
Other new affiliated packages include \texttt{agnpy} \cite{agnpy} for AGN jets,
\texttt{statmorph}  \cite{statmorph}for fitting galactic morphological diagnostics,
\texttt{dust\_extinction} for modeling interstellar dust extinction,
\texttt{feets} for extracting features from time series data, and
\texttt{corral} \cite{corral} for managing data intensive parallel pipelines.
\texttt{casaformats-io} provides infrastructure for reading data stored in CASA table formats.
\texttt{saba} gives an interface to the Sherpa \citep{sherpa} fitting routines,
\texttt{BayesicFitting} \cite{BayesicFitting} provides an interface for generic Bayesian inference,
and \texttt{sbpy} \cite{sbpy} enables calculations for asteroid and
cometary astrophysics. Finally, \texttt{synphot} \cite{synphot} provides an interface for
synthetic photometry.
% \citep{Mommert2019}
